\cvsection{Projects}

\begin{cventries}
  \cventry
    {} % Empty position
    {Delhi Government School Ranking website } % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {A website which ranks the school on the basis of their contribution in achieving the sustainable development by considering factors like lab equipments , passing percentage of students ,percentage of greenery in the campus etc .}
		\item {The project uses \textbf{Nodejs} backend, \textbf{CSS}, \textbf{JavaScript} frontend, \textbf{MongoDB} database with \textbf{EJS} as templating engine.}
      \end{cvitems}
    }

  \cventry
    {} % Empty position
    {Women Help website } % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item { An employment exchange portal for suppressed women with the required job skills where recruiters can post about the job availability .This site also helps women by providing the financial help in money management.}
		\item {The project uses \textbf{Nodejs} backend, \textbf{CSS}, \textbf{JavaScript} frontend, \textbf{MongoDB} database with \textbf{EJS} as templating engine.}
      \end{cvitems}
    }
    
  \cventry
    {} % Empty position
    {Image Captioner } % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item { A model which gives captions describing the input image.}
    		\item {State of the art \textbf{Resnet50 model} was used to extract features from an image, \textbf{Word2Vec} representations for the captions for the input to  a non-sequential \textbf{RNN/LSTM} model for predicting the caption.
            }
      \end{cvitems}
    }
  \cventry
    {} % Empty position
    {AI Music Generator } % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item { A model which generates MIDI music files starting from any input 100 notes/chords.}
    	\item {This model generates new music by training on the \textbf{music MIDI files} of the already existing songs which are decomposed into individual chords and notes into group of 100 which are input into the \textbf{RNN/LSTM} model which outputs the predicted chords/notes.}
      \end{cvitems}
    }
  \cventry
    {} % Empty position
    {Clothing Image Classifier} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item { A model which classifies images of fashion items into their sub-classes}
    	\item {A model is trained on the MNIST fashion training dataset using \textbf{CNNs(Convolutional Neural Networks)} consisting of \textbf{convolutional , pooling ,dropout and dense layers} which classifies the image of a fashion item into one of the ten classes. }
      \end{cvitems}
    }
  \cventry
    {} % Empty position
    {Parkinson's Disease Predictor} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {This model predicts whether a person has Parkinson's disease(2nd most degenerative neural disorder after Alzheimer's) or not, using \textbf{xgboost}.}
      \end{cvitems}
    }
\end{cventries}